---
title: "ESM 206 Lab 8"
author: "Ridhima chaudhuri"
date: "11/15/2021"
output: html_document
---

```{r setup, include=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning= FALSE)
```

```{r}
library(tidyverse)
library(janitor)
library(here)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)

```
```{r}
homes <- read_csv(here("data", "slo_homes.csv")) %>%
  janitor::clean_names()
print(homes)
```


A little bit of cleaning

Make a subset called home_sub which only contins observations  (rows) where the city is :
- San louis obispo
-Arroyo Grande
-Atascadero
-Santa Maria-Orcutt


```{r}

homes_sub <- homes %>%
  filter(city %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```
## Do a little bit of exploring

summary statistics (home price, based on city and sale status):

- Find and return in a nice summary table the mean and standard deviation of home price, grouped by city ansd sale status

```{r}
homes_sub %>%
  group_by(city, status) %>%
  summarize(mean_price= mean(price, na.rm= TRUE), sd_price= sd(price, na.rm = TRUE))

# actually I don't even want to run this code: eval= FALSE


ggplot(data= homes_sub, aes(x=price)) +
  geom_density(aes(color=city, fill=city), alpha=0.3) + scale_x_continuous(limits = c(0,3e6))#mapping a variable to an aesthetic so inside the aes 

```
this plot is exploratory. higher density of houses for lower price for santa maria. 

Explore the relationship (visual data exploration) between square footage and home price. Change the point color by city, and the point shape by sale status.

```{r}
ggplot(data= homes_sub, aes(x = sq_ft, y = price)) +geom_point() + geom_smooth(method=lm)
```
## Model the relationship with home price as dependent variable ( that is the outcome variable)

```{r}
homes_lm1 <- lm(price ~ city + bedrooms + bathrooms+ sq_ft + price_per_sq_ft + status , data = homes_sub)


```

# Make a subset that only contains the quantitative variables
```{r}
 homes_quant <- homes_sub %>%
  select(price: price_per_sq_ft)
homes_cor <- cor(homes_quant)
homes_cor

corrplot(homes_cor, method = 'ellipse')

#How would i explore the diagnostic plots?
  
plot(homes_lm1)  
```
Try another model where we simplify this a bit:

-city
-sq_ft
-status

```{r}
homes_lm2 <- lm(price ~ city + sq_ft + status, data = homes_sub)
plot(homes_lm2)
```
 Adjusted R squared value of 0.8457 interpretation: 84% of the variance in home price is explained by the variables - city, bedroom bathroom price per sq foot, status. it accounts for the fact that model fit will increase solely by adding variables. 

Find the AIC value of each model:

```{r}
AIC(homes_lm1)
AIC(homes_lm2)
```


A lower AIC value indicates a better fit between model fit and complexity. 

Try another permutation of this model that you think might make sense, check out and compare the model fit, outputs and AIC value.
```{r}
homes_lm3 <- lm(price ~ sq_ft +city + bedrooms + status, data = homes_sub)

summary(homes_lm3)
AIC(homes_lm3)
```

Use modelsummary to show model outputs side-by-side

if you use model summary to return model outputs of multiple models, it wants you to feed it to it as a list.
```{r}
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```

## Start making predicitions with this model

Use 'broom::augment()'

```{r}
homes_predicited <- augment(homes_lm1)
```
Use the predict() function to try out your model on new scenarios you create. 


# MY UPDATE!!!
